The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
fix last few refs

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
advanced to the point where relocations can be programmed to occur as frequently
as each second [@Börger_2016], a practice which has been applied to questions of
collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
technology, including unmanned aerial vehicles and satellites, can be used to
track the fine-scale movements of groups over large distances and time scales
[@Torney_2018]. Using technology to infer behaviour has therefore become
standard operating procedure for many species in many systems. Our ability to
collect and process remotely sensed data and infer social processes based on
animal movement provides an opportunity to use multilayer social network
analysis to answer complex questions about animal socioecology.

@@

Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
advances have lead to increased data complexity and resolution. Remotely sensed
imagery collected by modern satellites provide, for example, 10 m spatial
resolution optical imagery at a temporal revisit period of five days at the
equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
at a higher temporal resolution [@Börger_2016]. Given this increased
availability of complex data, it is important to consider using a broad
continuum of scales to fully capture ecological processes, carefully select and
combine sources of data with different temporal and spatial scales, and
establish a clear link between scales of observation and meaningful biology.

>>>>

Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
advanced to the point where relocations can be programmed to occur as frequently
as each second [@B_rger_2016], a practice which has been applied to questions of
collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
technology, including unmanned aerial vehicles and satellites, can be used to
track the fine-scale movements of groups over large distances and time scales
[@Torney_2018]. Using technology to infer behaviour has therefore become
standard operating procedure for many species in many systems. Our ability to
collect and process remotely sensed data and infer social processes based on
animal movement provides an opportunity to use multilayer social network
analysis to answer complex questions about animal socioecology.

@@

Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
advances have lead to increased data complexity and resolution. Remotely sensed
imagery collected by modern satellites provide, for example, 10 m spatial
resolution optical imagery at a temporal revisit period of five days at the
equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
at a higher temporal resolution [@B_rger_2016]. Given this increased
availability of complex data, it is important to consider using a broad
continuum of scales to fully capture ecological processes, carefully select and
combine sources of data with different temporal and spatial scales, and
establish a clear link between scales of observation and meaningful biology.
